An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-05-25 neurips-19/poly-embed.tex
some notes for proof update

\usepackage{mathtools, amsmath, amssymb, amsthm, graphicx, verbatim}
%\usepackage[thmmarks, thref, amsthm]{ntheorem}
\usepackage{color}
\definecolor{darkblue}{rgb}{0.0,0.0,0.2}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}
\usepackage{wrapfig}
\usepackage[font=small]{caption}
\usepackage{subcaption}
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}
\usepackage{xspace}

\usetikzlibrary{calc}
\newcommand{\Comments}{0}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{}%TURN OFF FOR NOW \mytodo{gray}{#1}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi

@@

\newcommand{\hinge}{L_{\mathrm{hinge}}}
\newcommand{\ellzo}{\ell_{\text{0-1}}}
\newcommand{\ellabs}[1]{\ell_{#1}}
\newcommand{\elltopk}{\ell_{\text{top-$k$}}}

@@

We augment this literature by studying a particularly natural approach for finding convex surrogates, wherein one ``embeds'' a discrete loss.
Specifically, we say a convex surrogate $L$ embeds a discrete loss $\ell$ if there is an injective embedding from the discrete reports (predictions) to a vector space such that (i) the original loss values are recovered, and (ii) a report is $\ell$-optimal if and only if the embedded report is $L$-optimal.
If this embedding can be extended to a calibrated link function, which maps approximately $L$-optimal reports to $\ell$-optimal reports, consistency follows~\cite{agarwal2015consistent}.
Common examples which follow this general construction include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above.

@@

\paragraph{Related works.}
The literature on convex surrogates focuses mainly on smooth surrogate losses~\cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite}.
Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems\cite{yang2018consistency,yu2018lovasz,lapin2015top}.
%\jessiet{Do we want the SVM (Boser) cite?}\raft{Basically anything we talk about in the examples. removed hari from this link since we mention it next}
A notable addition to this literature is~\citet{ramaswamy2018consistent}, who argue that nonsmooth losses may enable dimension reduction of the prediction space (range of the surrogate hypothesis) relative to smooth losses, illustrating this conjecture with a surrogate for \emph{abstain loss} needing only $\log n$ dimensions for $n$ labels, whereas the best known smooth loss needs $n-1$.
Their surrogate is a natural example of an embedding (cf.~Section~\ref{sec:abstain}), and serves as inspiration for our work.

@@

We assume that a given discrete prediction problem, such as classification, is given in the form of a \emph{discrete loss} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r$ from a finite set $\R$ to the vector of loss values $\ell(r) = (\ell(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
We will assume throughout that the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\simplex$.
Similarly, surrogate losses will be written $L:\reals^d\to\reals^\Y_+$, typically with reports written $u\in\reals^d$.
\btw{Cut generic loss}%(A generic loss will be written $L:\R\to\reals^\Y$.)
We write the corresponding expected loss when $Y \sim p$ as $\inprod{p}{\ell(r)}$ and $\inprod{p}{L(u)}$.
The \emph{Bayes risk} of a loss $L:\reals^d\to\reals^\Y_+$ is the function $\risk{L}:\simplex\to\reals_+$ given by $\risk{L}(p) := \inf_{u\in\reals^d} \inprod{p}{L(u)}$; naturally for discrete losses we write $\risk{\ell}$ (and the infimum is over $\R$).

@@

Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex; we therefore briefly recall the relevant definitions.
In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
A \emph{polytope} is a bounded polyhedral set.
A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.
%
\begin{definition}[Polyhedral loss]
  A loss $L: \reals^d \to \reals^{\Y}_+$ is \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
\end{definition}
%
For example, hinge loss is polyhedral, whereas logistic loss is not.

@@

To make headway, we will appeal to concepts and results from the property elicitation literature, which elevates the \emph{property}, or map from distributions to optimal reports, as a central object to study in its own right.
In our case, this map will often be multivalued, meaning a single distribution could yield multiple optimal reports.
(For example, when $p=(1/2,1/2)$, both $y=1$ and $y=-1$ optimize 0-1 loss.)
To this end, we will use double arrow notation to mean a mapping to all nonempty subsets, so that $\gamma: \simplex \toto \R$ is shorthand for $\Gamma: \simplex \to 2^{\R} \setminus \emptyset$.
See the discussion following Definition~\ref{def:elicits} for conventions regarding $\R$, $\Gamma$, $\gamma$, $L$, $\ell$, etc.

\begin{definition}[Property, level set]\label{def:property}
  A \emph{property} is a function $\Gamma:\simplex\toto\R$.
  The \emph{level set} of $\Gamma$ for report $r$ is the set $\Gamma_r := \{p : r \in \Gamma(p)\}$.
\end{definition}

Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
\btw{Finite property note commented out}%(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
For example, the \emph{mode} is the %finite
property $\mode(p) = \argmax_{y\in\Y} p_y$, and captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
% This terminology comes from the information elicitation \jessiet{information vs property... do we care?}\raft{we could also say economics literature; not ``property'' though since that doesn't offer an explanation of the word ``elicits''} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.

\begin{definition}[Elicits]
  \label{def:elicits}
  A loss $L:\R\to\reals^\Y_+$, \emph{elicits} a property $\Gamma:\simplex \toto \R$ if
  \begin{equation}
    \forall p\in\simplex,\;\;\;\Gamma(p) = \argmin_{r \in \R} \inprod{p}{L(r)}~.
  \end{equation}
  As $\Gamma$ is uniquely defined by $L$, we write $\prop{L}$ to refer to the property elicited by a loss $L$.
\end{definition}

For finite properties (those with $|\R|<\infty$) and discrete losses, we will use lowercase notation $\gamma$ and $\ell$, respectively, with reports $r\in\R$; for surrogate properties and losses we use $\Gamma$ and $L$, with reports $u\in\reals^d$.
% For finite properties (those with $|\R|<\infty$) and discrete losses, we will use lowercase notation $\gamma:\simplex\toto\R$ and $\ell:\R\toto\reals^\Y_+$, respectively, with reports $r\in\R$; for surrogate properties and losses we use $\Gamma:\simplex\toto\reals^d$ and $L:\reals^d\toto\reals^\Y_+$, with reports $u\in\reals^d$.
For general properties and losses, we will also use $\Gamma$ and $L$, as above.

% Often we will work with two properties simultaneously, a finite property $\gamma:\simplex\toto\R$, and its embedded version $\Gamma:\simplex\toto\reals^d$.
% In this case, we write the embedded reports as $u\in\reals^d$, reserving $r\in\R$ for the finite property.

@@

To assess whether a surrogate and link function align with the original loss, we turn to the common condition of \emph{calibration}.
Roughly, a surrogate and link are calibrated if the best possible expected loss achieved by linking to an incorrect report is strictly suboptimal.
\btw{Separated stuff commented out}
% , which require that the excess loss of some report is bounded by (a constant times) the excess loss of the linked report.

@@

\begin{definition}
  \label{def:calibrated}
  Let original loss $\ell:\R\to\reals^\Y_+$, proposed surrogate $L:\reals^d\to\reals^\Y_+$, and link function $\psi:\reals^d\to\R$ be given.
  We say $(L,\psi)$ is \emph{calibrated} with respect to $\ell$ if
for all $p \in \simplex$,
  \begin{equation}
    \label{eq:calibrated}
  \inf_{u \in \reals^d : \psi(u) \not\in \gamma(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)}~.
  \end{equation}
\end{definition}
It is well-known that calibration implies \emph{consistency}, in the following sense (cf.~\cite{agarwal2015consistent}).
Given feature space $\X$, fix a fixed distribution $D \in \Delta(\X\times\Y)$.
Let $L^*$ be the best possible expected $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
Then $(L,\psi)$ is consistent if a sequence of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, then the $\ell$-loss of $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$.
As Definition~\ref{def:calibrated} does not involve the feature space $\X$, we will drop it for the remainder of the paper.

@@

To illustrate the idea of embedding, let us examine hinge loss in detail as a surrogate for 0-1 loss for binary classification.
Recall that we have $\R = \Y = \{-1, +1\}$, with $\hinge(u)_y = (1 - uy)_+$ and $\ellzo(r)_y := \Ind{r\neq y}$, typically with link function $\psi(u) = \sgn(u)$.
We will see that hinge loss embeds (2 times) 0-1 loss, via the embedding $\varphi(r) = r$.
For condition (i), it is straightforward to check that $\hinge(r)_y = 2\ellzo(r)_y$ for all $r,y\in\{-1,1\}$.
% First, consider that
% \begin{align*}
% 	\ellzo(-1) = (0,1) && \ellzo(1) = (1,0)\\
% 	L_{hinge}(-1) = (0,2) && L_{hinge}(1) = (2,0)\\
% \end{align*}
% Therefore, $L_{hinge}$ is twice $\ellzo$ for each $r \in \R$.
For condition (ii), let us compute the property each loss elicits, i.e., the set of optimal reports for each $p$:
\[
\prop{\ellzo}(p) = \begin{cases}
1 & p_1 > 1/2 \\
\{-1,1\} & p_1 = 1/2\\
-1 & p_1 < 1/2
\end{cases}
\qquad
\prop{L_{hinge}}(p) = \begin{cases}
[1,\infty) & p_1 = 1\\
1 & p_1 \in (1/2,1) \\
[-1,1] & p_1 = 1/2\\
-1& p_1 \in (0, 1/2)\\
(-\infty, -1]& p_1 = 0
\end{cases}~.
\]
% Now, take the embedding $\varphi$ to be the identity.  % := r$ if $r \in [-1,1]$, and $\sgn(r)$ otherwise.
In particular, we see that $-1 \in \prop{\ellzo}(p) \iff p_1 \in [0, 1/2] \iff -1 \in \prop{\hinge}(p)$, and $1 \in \prop{\ellzo}(p) \iff p_1 \in [1/2,1] \iff 1 \in \prop{\hinge}(p)$.
With both conditions of Definition~\ref{def:loss-embed} satisfied, we conclude that $\hinge$ embeds $2\ellzo$.
In this particular case, it is known $(\hinge,\psi)$ is calibrated for $\psi(u) = \sgn(u)$; we address in Section~\ref{sec:calibration} the interesting question of whether embeddings lead to calibration in general.

@@

    \btw{RF: This is on the informal side, mostly because of the ``working in the affine hull'' bit.  It can all be formalized though, probably should be for the journal version: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.}
  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
  In what follows, we implicitly work in the affine hull of $\simplex$, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the (relative) interior of $\simplex$.
  Since $\ell$ is discrete, $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
  The projection of its epigraph $E_\ell$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$.

@@

\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}
  If $L$ embeds $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$, and its proof already argued that $\risk{\ell}$ is polyhedral.
  For the converse, let $\risk{L}$ be polyhedral; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
  The projection of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
  Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
  Defining $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$.
  % The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
  % Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
  % Call the set of full-dimensional cells in this power diagram $F$, and note that $F$ is finite since it defined by a projection of a polyhedral function.
  % For each $f \in F$, there is a distribution $p \in \inter{f}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
  % Pick some $u_f \in \argmin_{u' \in \U}L(u', p)$.
  % The coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u_f)$.
  % Repeat this process for every facet, and denote $\R := \{u_f\}_{f \in F}$.
  % Since $\cup f = \simplex$, and each $f$ isequal to $\Gamma_{u_f}$ for some $u_f \in \reals^d$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
% <<<<<<< HEAD
%   For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
%   By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
%   Since $\ell$ is discrete, $\risk{\ell}$ is polyhedral as the minimum of a finite set of linear functions in $\simplex$. %\raf{do we know? okay, we do---but why?}.
%   Therefore, $\risk{L}$ is polyhedral.
%   The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
%   Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
%   Call the set of full-dimensional cells in this power diagram $\U'$, where each $U \in \U'$ corresponds to $\Gamma_u$ for some $u \in \U$.
%   For each $u \in \U'$, there is a distribution $p \in \inter{\Gamma_u}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
%   Pick some $u \in \argmin_{u' \in \U}L(u', p)$.
%   As before, the coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u)$.
%   Repeat this process for every facet.
%   Since $\cup_{\U'} \Gamma_u = \simplex$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
% =======
\end{proof}

Combining Proposition~\ref{prop:embed-risk-poly} with the observation that polyhedral losses have polyhedral Bayes risks (Lemma~\ref{lem:poly-loss-poly-risk}), we obtain the first direction of our equivalence between polyhedral losses and embedding.

>>>>

\usepackage{mathtools, amsmath, amssymb, amsthm, graphicx, verbatim}
%\usepackage[thmmarks, thref, amsthm]{ntheorem}
\usepackage{color}
\definecolor{darkblue}{rgb}{0.0,0.0,0.2}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}
\usepackage{xspace}

\usetikzlibrary{calc}
\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{}%TURN OFF FOR NOW \mytodo{gray}{#1}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi

@@

\newcommand{\hinge}{L_{\mathrm{hinge}}}
\newcommand{\ellzo}{\ell_{\text{0-1}}}
\newcommand{\ellabs}[1]{\ell_{#1}}

@@

We augment this literature by studying a particularly natural approach for finding convex surrogates, wherein one ``embeds'' a discrete loss.
Specifically, we say a convex surrogate $L$ embeds a discrete loss $\ell$ if there is an injective embedding from the discrete reports (predictions) to a vector space such that (i) the original loss values are recovered, and (ii) a report is $\ell$-optimal if and only if the embedded report is $L$-optimal.
If this embedding can be extended to a calibrated link function, which maps approximately $L$-optimal reports to $\ell$-optimal reports, consistency follows~\cite{agarwal2015consistent}.
Common examples which follow this general construction include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above. \jessiet{Really 0-2 loss, but that seems like an unimportant nuance.}

@@

\subsection{Related works}
\raf{Let's dump a bunch of citations and not worry about going into detail.  I'll throw in a skeleton.}

The literature on convex surrogates focuses mainly on smooth surrogate losses~\raf{DKR;many more...}\jessiet{DKR, some of Bob's added.}\cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite}.
Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems\cite{ramaswamy2018consistent, boser1992training}\raf{cites} \jessiet{Do we want the SVM (Boser) cite?}.
A notable addition to this literature is~\citet{ramaswamy2018consistent}, who argue that nonsmooth losses may enable dimension reduction of the prediction space (range of the surrogate hypothesis) relative to smooth losses, illustrating this conjecture with a surrogate for \emph{abstain loss} needing only $\log n$ dimensions for $n$ labels, whereas the best known smooth loss needs $n-1$.
Their surrogate is a natural example of an embedding (cf.~Section~\ref{sec:abstain}), and serves as inspiration for our work.

@@

We assume that a given discrete prediction problem, such as classification, is given in the form of a \emph{discrete loss} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r$ from a finite set $\R$ to the vector of loss values $\ell(r) = (\ell(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
We will assume throughout that the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\simplex$.
Similarly, surrogate losses will be written $L:\reals^d\to\reals^\Y_+$, typically with reports written $u\in\reals^d$.
\raft{Cut generic loss}%(A generic loss will be written $L:\R\to\reals^\Y$.)
We write the corresponding expected loss when $Y \sim p$ as $\inprod{p}{\ell(r)}$ and $\inprod{p}{L(u)}$.
The \emph{Bayes risk} of a loss $L:\reals^d\to\reals^\Y_+$ is the function $\risk{L}:\simplex\to\reals_+$ given by $\risk{L}(p) := \inf_{u\in\reals^d} \inprod{p}{L(u)}$; naturally for discrete losses we write $\risk{\ell}$ (and the infimum is over $\R$).

@@

Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex; we therefore briefly recall the relevant definitions.
In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
A \emph{polytope} is a bounded polyhedral set.
A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.
%
\begin{definition}[Polyhedral loss]
  A loss $L: \reals^d \to \reals^{\Y}_+$ is a \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
\end{definition}
%
For example, hinge loss is polyhedral, whereas logistic loss is not.

@@

To make headway, we will appeal to concepts and results from the property elicitation literature, which elevates the \emph{property}, or map from distributions to optimal reports, as a central object to study in its own right.
In our case, this map will often be multivalued, meaning a single distribution could yield multiple optimal reports.
(For example, when $p=(1/2,1/2)$, both $y=1$ and $y=-1$ optimize 0-1 loss.)
To this end, we will use double arrow notation to mean a mapping to all nonempty subsets, so that $\gamma: \simplex \toto \R$ is shorthand for $\gamma: \simplex \to 2^{\R} \setminus \emptyset$.

\bo{The following is not ideal because everywhere else in the paper, we always use $\R$ with $\gamma$ and $\reals^d$ with $\Gamma$} \jessie{Is this better?}
\begin{definition}[Property, level set]\label{def:property}
  A \emph{property} is a function $\Gamma:\simplex\toto\U$.
  The \emph{level set} of $\Gamma$ for report $u$ is the set $\Gamma_u := \{p : u \in \Gamma(p)\}$.
\end{definition}

Thus, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
\raft{Finite property note commented out}%(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
For example, the \emph{mode} is the %finite
property $\mode(p) = \argmax_{y\in\Y} p_y$, and captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
% This terminology comes from the information elicitation \jessiet{information vs property... do we care?}\raft{we could also say economics literature; not ``property'' though since that doesn't offer an explanation of the word ``elicits''} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.

\begin{definition}[Elicits]
  A loss $L:\R\to\reals^\Y_+$, \emph{elicits} a property $\Gamma:\simplex \toto \R$ if
  \begin{equation}
    \forall p\in\simplex,\;\;\;\Gamma(p) = \argmin_{r \in \R} \inprod{p}{L(r)}~.
  \end{equation}
  As $\Gamma$ is uniquely defined by $L$, we write $\prop{L}$ to refer to the property elicited by a loss $L$.
\end{definition}

For finite properties (those with $|\R|<\infty$) and discrete losses, we will use lowercase notation $\gamma$ and $\ell$, respectively, while $\Gamma$ and $L$ will be used for surrogate (or general) properties and losses.
% Often we will work with two properties simultaneously, a finite property $\gamma:\simplex\toto\R$, and its embedded version $\Gamma:\simplex\toto\reals^d$.
% In this case, we write the embedded reports as $u\in\reals^d$, reserving $r\in\R$ for the finite property.

@@

To assess whether a surrogate and link function align with the original loss, we turn to the common condition of \emph{calibration}.
Roughly, a surrogate and link are calibrated if the best possible expected loss achieved by linking to an incorrect report is strictly suboptimal.
\raft{Separated stuff commented out}
% , which require that the excess loss of some report is bounded by (a constant times) the excess loss of the linked report.

@@

\begin{definition}
  \label{def:calibrated}
  Let original loss $\ell:\R\to\reals^\Y_+$, proposed surrogate $L:\reals^d\to\reals^\Y_+$, and link function $\psi:\reals^d\to\R$ be given.
  We say $(L,\psi)$ is \emph{calibrated} with respect to $\ell$ if
for all $p \in \simplex$,
  \begin{equation}
    \label{eq:calibrated}
  \inf_{u \in \reals^d : \psi(u) \not\in \gamma(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)}~.
  \end{equation}
\end{definition}
It is well-known that calibration implies \emph{consistency}, in the sense that
\raf{rough definition here}~\cite{agarwal2015consistent}.

@@

To illustrate the idea of embedding, let us examine hinge loss in detail as a surrogate for 0-1 loss for binary classification.
Recall that we have $\R = \Y = \{-1, +1\}$, with $\hinge(u)_y = (1 - uy)_+$ and $\ellzo(r)_y := \Ind{r\neq y}$, typically with link function $\psi(u) = \sgn(u)$.
We will see that hinge loss embeds (2 times) 0-1 loss, via the embedding $\varphi(r) = r$.
For condition (i), it is straightforward to check that $\hinge(r)_y = 2\ellzo(r)_y$ for all $r,y\in\{-1,1\}$.
% First, consider that 
% \begin{align*}
% 	\ellzo(-1) = (0,1) && \ellzo(1) = (1,0)\\
% 	L_{hinge}(-1) = (0,2) && L_{hinge}(1) = (2,0)\\
% \end{align*}
% Therefore, $L_{hinge}$ is twice $\ellzo$ for each $r \in \R$.
For condition (ii), let us compute the property each loss elicits (i.e. the set of optimal reports for each $p$):
\[
\prop{\ellzo}(p) = \begin{cases}
1 & p_1 > 1/2 \\
\{-1,1\} & p_1 = 1/2\\
-1 & p_1 < 1/2
\end{cases}
\qquad 
\prop{L_{hinge}}(p) = \begin{cases}
[1,\infty) & p_1 = 1\\
1 & p_1 \in (1/2,1) \\
[-1,1] & p_1 = 1/2\\
-1& p_1 \in (0, 1/2)\\
(-\infty, -1]& p_1 = 0
\end{cases}~.
\]
% Now, take the embedding $\varphi$ to be the identity.  % := r$ if $r \in [-1,1]$, and $\sgn(r)$ otherwise.
In particular, we see that $-1 \in \prop{\ellzo}(p) \iff p_1 \in [0, 1/2] \iff -1 \in \prop{\hinge}(p)$, and $1 \in \prop{\ellzo}(p) \iff p_1 \in [1/2,1] \iff 1 \in \prop{\hinge}(p)$.
With both conditions of Definition~\ref{def:loss-embed} satisfied, we conclude that $\hinge$ embeds $2\ellzo$.
In this particular case, it is known $(\hinge,\psi)$ is calibrated for $\psi(u) = \sgn(u)$; we address in Section~\ref{sec:calibration} the interesting question of whether embeddings lead to calibration in general.

@@

  %\raft{Jessie: I commented out your version below the proof.  What I have is on the informal side (so not necessarily better than what you had), mostly because of the ``working in the affine hull'' bit.  It can all be formalized though: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.  I can explain more on a call...}
  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
  In what follows, we implicitly work in the affine hull of $\simplex$, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the (relative) interior of $\simplex$.
  Since $\ell$ is discrete, $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
  The projection of its epigraph $E_\ell$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$.

@@

\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}
  If $L$ embeds $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$, and its proof already argued that $\risk{\ell}$ is polyhedral.
  For the converse, let $\risk{L}$ be polyhedral; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
  The projection of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
  Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
  Defining $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$.
  % The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
  % Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
  % Call the set of full-dimensional cells in this power diagram $F$, and note that $F$ is finite since it defined by a projection of a polyhedral function.
  % For each $f \in F$, there is a distribution $p \in \inter{f}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
  % Pick some $u_f \in \argmin_{u' \in \U}L(u', p)$.
  % The coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u_f)$.
  % Repeat this process for every facet, and denote $\R := \{u_f\}_{f \in F}$.
  % Since $\cup f = \simplex$, and each $f$ isequal to $\Gamma_{u_f}$ for some $u_f \in \reals^d$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.

% <<<<<<< HEAD
%   For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
%   By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
%   Since $\ell$ is discrete, $\risk{\ell}$ is polyhedral as the minimum of a finite set of linear functions in $\simplex$. %\raf{do we know? okay, we do---but why?}.
%   Therefore, $\risk{L}$ is polyhedral.

%   The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
%   Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
%   Call the set of full-dimensional cells in this power diagram $\U'$, where each $U \in \U'$ corresponds to $\Gamma_u$ for some $u \in \U$. 
%   For each $u \in \U'$, there is a distribution $p \in \inter{\Gamma_u}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
%   Pick some $u \in \argmin_{u' \in \U}L(u', p)$.
%   As before, the coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u)$.
%   Repeat this process for every facet.
%   Since $\cup_{\U'} \Gamma_u = \simplex$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
% =======
\end{proof}

Combining Proposition~\ref{prop:embed-risk-poly} with the following observation that polyhedral losses have polyhedral Bayes risks, we obtain the first direction of our equivalence between polyhedral losses and embedding.
